### 2017-01-12 paper/evaluation.tex
fixes and pass on text

A Maven project may contain several sub-modules with multiple \pomf{}
files. We considered only projects with a \pomf{} file located in the
root directory.  As of December 30th 2016, our search criteria
returned \numSubjsTotal{} subjects. From the \numSubjsTotal{}
downloaded projects, 46 were not Maven projects (or did not have a
\pomf{} in the root directory) and 159 were in a unstable revision.
From these 159 unstable subjects, \Jbc{elaborate what is unstable (eg,
(1) how many could not resolve dependencies? (2) how many could not
compile sources and tests? (3) could not run tests due to incompatible
testing environment?}. Our final set consists in \numSubjs{} testable
subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects} and
compared the elapsed time to run their tests.
Figure~\ref{fig:mvn-execution} shows the commands used in our script
to test each subject. The main loop (lines 5-11) iterates over the
list of subjects and invokes Maven in separated steps (lines 7-9). To
avoid inflating the measured time we executed Maven in different
steps: we first compiled the source and test files (line 7), made all
dependencies available locally (line 8) and later, we ran the tests in
offline mode (line 9) to bypass package updates. After the execution,
we used a regular expression on the output log to extract the elapsed
time (line 10). Before collecting the time cost, we executed all
subjects and randomly selected 100 logs to inspect and identify
non-related tasks (\eg, \emph{javadoc} generation and static analysis)
to ignore during the experiment (lines 1-3).  To avoid noise from
operating system events, we used a dedicated server remotely via SSH
with the operating system running only essential services (\eg, the
SSH server). In addition, we configured the \CodeIn{isolcpus} option
from the Linux Kernel \cite{linux-kernel} to isolate six virtual CPUs
to execute our experiment and the remaining CPUs to run the operating
system. By isolating a set of virtual CPUs, we prevent
context-switching from experiment processes and OS-related processes.

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjsTotal{} projects we analyzed.  However, use of parallelism
does not assure speedups on those projects.  We analyzed one sensible
factor that is critical to the effectiveness of parallelism: the
amount of tests that dominate execution time.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

We evaluated the dispersion of time distributions (one distribution
per project) to aswer research question RQ2.  To measure dispersion
\emph{across} projects we used Relative Standard Deviation
(RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
analyze each project in isolation, the standard deviation of a
distribution ($\sigma$) would suffice to quantify how dispersed the
(time) distribution is.  However, in our case, we would like to be
able to compare and summarize dispersion across projects.  The RSD,
which is obtained dividing the standard deviation by the mean ($\mu$)
of a distribution, provides such normalization effect.  This metric
provides a lower bound (zero) but not an upper bound (somewhere close
to 1).  The smaller (larger) the value of RSD the more (less) uniform
the distribution is.  Consequently, ignoring other factors that affect
performance of parallelization (e.g., CPU/IO ratio), the lower the
value of RSD the more parallelizable a test suite should be.

@@

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group}
            & \multirow{2}{*}{\# \pomf{}}
            & \# \pomf{} matched
            & \# projects matched\\%
        % 2nd row - empty cell
            & % empty cell
            & (false-positives)
            & / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19 / \numLong{}\\%
        Medium & 1238 & 30 (5) & 22 / \numMed{}\\%
        \midrule%
        Total & \pomMedLong{} & \numPomMatched{} (6) & \numProjectsPar{} / \numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallelization settings in build files: the
    first column indicates the group of projects according to their
    time cost; the second column indicates the number of build files;
    the third column is the subset of files with parallelization
    keywords; the last column indicates the ratio of projects with
    parallelism support.}
    \label{tab:inspection-table} 
\end{figure}

@@

From the \numProjectsPar{} projects identified above, we investigated
further the \numPomMatchedValid{} build files with parallel settings.
We analyzed the support and distribution of parallel modes from this
subset of projects. To calculate the distribution of parallel modes,
we considered only the presence of the mode in at least one of the
project settings.  Recall that a build file may contain more than one
parallel setting and a project may contain several sub-modules with
build files.  In case the value of a parallel option is resolved
dynamically (\eg, via command-line argument or system variable) we
compute all modes related to the option. For instance, depending on
the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes} summarizes our findings.

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallel modes
    identified in a subset of \numProjectsPar{} projects. A single
    project may have support to more than one parallel mode.}
\end{figure}

>>>>

A Maven project may contain several sub-modules with multiple \pomf{}
files. We considered only projects with a \pomf{} file located in the
root directory.  As of December 30th 2016, our search criteria
returned 615 subjects. From the 615 downloaded projects, 46 were not
Maven projects (or did not have a \pomf{} in the root directory) and
159 were in a unstable revision.  From these 159 unstable subjects,
\Jbc{elaborate what is unstable (\eg, (1) how many could not resolve
dependencies? (2) how many could not compile sources and tests? (3)
could not run tests due to incompatible testing environment?}. Our
final set consists in \numSubjs{} testable subjects.

@@

To evaluate the frequency of time-consuming regression tests, we
considered the \numSubjs{} subjects from Section~\ref{sec:subjects}
and compared the elapsed time to run their tests. \Jbc{Be clear about
checking the elapsed time }.  Figure~\ref{fig:mvn-execution} shows the
commands used in our script to test each subject. The main loop (lines
5-11) iterates over the list of subjects and invokes Maven in
separated steps (lines 7-9). To avoid inflating the measured time we
executed Maven in different steps: we first compiled the source and
test files (line 7), made all dependencies available locally (line 8)
and later, we ran the tests in offline mode (line 9) to bypass package
updates. After the execution, we used a regular expression on the
output log to extract the elapsed time (line 10). Before collecting
the time cost, we executed all subjects and randomly selected 100 logs
to inspect and identify non-related tasks (\eg, \emph{javadoc}
generation and static analysis) to ignore during the experiment (lines
1-3).  To avoid noise from operating system events, we used a
dedicated server remotely via SSH with the operating system running
only essential services (\eg, the SSH server). In addition, we
configured the \CodeIn{isolcpus} option from the Linux Kernel
\cite{linux-kernel} to isolate six virtual CPUs to execute our
experiment and the remaining CPUs to run the operating system. By
isolating a set of virtual CPUs, we prevent context-switching from
experiment processes and OS-related processes.

@@

Section~\ref{sec:rqA} showed that medium and long-running projects are
not uncommon; they account to nearly \percentMedLongRunning{} of the
\numSubjs{} projects we analyzed.  However, use of parallelism
does not assure speedups on those projects.  We analyzed one sensible
factor that is critical to the effectiveness of parallelism: the
amount of tests that dominate execution time.  In the limit, if cost
is dominated by a single test, it is unlikely that parallelization
will be beneficial as a test method is the smallest working unit in
test frameworks (see Section~\ref{sec:frameworks}).

@@

We evaluated the dispersion of time distributions (one distribution
per project) to answer research question \numRQB{}.  To measure
dispersion \emph{across} projects we used Relative Standard Deviation
(RSD)~\cite{everitt-book-stats-2010}.  Note that, if we were to
analyze each project in isolation, the standard deviation of a
distribution ($\sigma$) would suffice to quantify how dispersed the
(time) distribution is.  However, in our case, we would like to be
able to compare and summarize dispersion across projects.  The RSD,
which is obtained dividing the standard deviation by the mean ($\mu$)
of a distribution, provides such normalization effect.  This metric
provides a lower bound (zero) but not an upper bound (somewhere close
to 1).  The smaller (larger) the value of RSD the more (less) uniform
the distribution is.  Consequently, ignoring other factors that affect
performance of parallelization (e.g., CPU/IO ratio), the lower the
value of RSD the more parallelizable a test suite should be.

@@

\begin{figure}[ht!]
    \centering
    \begin{tabular*}{0.48\textwidth}{@{\extracolsep{\fill}}cccc}
        \toprule
        \multirow{2}{*}{Group} %1st row, 1st cell
            & \multirow{2}{*}{\# \pomf{}}
            & \# \pomf{} matched
            & \# projects matched\\%
        % 2nd row - empty cell
            & % empty cell
            & (false-positives)
            & / total\\%
        \midrule%
        Long   & 1613 & 79 (1) & 19 / \numLong{}\\%
        Medium & 1238 & 30 (5) & 22 / \numMed{}\\%
        \midrule%
        Total % last row, first cell
            & \pomMedLong{}
            & \numPomMatched{} (6)
            & \numProjectsPar{} / \numMedLong{}\\%
        \bottomrule%
    \end{tabular*}
    \caption{Presence of parallelization settings in build files: the
    first column indicates the group of projects according to their
    time cost; the second column indicates the number of build files;
    the third column is the subset of files with parallelization
    keywords; the last column indicates the ratio of projects with
    parallelism support.}
    \label{tab:inspection-table} 
\end{figure}

@@

From the \numProjectsPar{} projects identified above, we investigated
further the \numPomMatchedValid{} build files with parallel settings.
We analyzed the support and distribution of parallel modes from this
subset of projects. To calculate the distribution of parallel modes,
we considered only the presence of the mode in at least one of the
project settings.  Recall that a build file may contain more than one
parallel setting and a project may contain several sub-modules with
build files.  In case the value of a parallel option is resolved
dynamically (\eg, via command-line argument or system variable) we
compute all modes related to the option. For instance, depending on
the value, the \CodeIn{parallel} option can be \Seq{} (\CodeIn{none}),
\ParClassSeqMeth{} (\CodeIn{classes}), \SeqClassParMeth{},
(\CodeIn{methods}), and \ParClassParMeth{} (\CodeIn{all}).
Figure~\ref{fig:freqmodes} summarizes our findings. \Jbc{Given that we
checked each configuration, we could elaborate how these settings are
used.} \Fix{Missing conclusion: Fork the most used configuration}

\begin{figure}[h!]
    \centering
    \includegraphics[width=0.32\textwidth]{plots/barplot-modes.pdf}
    \caption{\label{fig:freqmodes}Distribution of parallel modes
    identified in a subset of \numProjectsPar{} projects (unused modes
    omitted). A single project may have support to more than one
    parallel mode.}
\end{figure}
